pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-20 article.tex
Reword MCRA prior

The goal of \verb;pirouette; is to measure the inference error BEAST2
makes from a given reconstructed phylogeny. For this measurement,
two models need to be specified: a generative and an inference model.
A generative model is a combination of site model, clock model and tree prior,
used to simulate alignments. An inference model is a combination of 
site model, clock model, tree prior, an optional node calibration prior
and setup of the Markov chain Monte Carlo (MCMC) algorithm, 
used to produce a posterior. Node calibration priors, called 'most
recent common ancestor' (MRCA) priors within BEAST2 allow, among others,
to specify a crown age.

>>>>

The goal of \verb;pirouette; is to measure the inference error BEAST2
makes from a given reconstructed phylogeny. For this measurement,
two models need to be specified: a generative and an inference model.
A generative model is a combination of site model, clock model and tree prior,
used to simulate alignments. An inference model is a combination of 
site model, clock model, tree prior, an optional node calibration prior
and setup of the Markov chain Monte Carlo (MCMC) algorithm, 
used to produce a posterior. Node calibration priors, called 'most
recent common ancestor' (MRCA) priors within BEAST2 allow to create a 
time-calibrated phylogeny, by specifying a normal distribution around
an expected time when two or more taxa's ancestors diversified.
